---
title: "README file of HELDA package"
author: Simon Corde
date: February 12, 2020
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# R package helda (HELpful functions for Data Analysis in R)

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/helda)](https://CRAN.R-project.org/package=helda)
[![Build Status](https://travis-ci.com/Redcart/helda.svg?branch=master)](https://travis-ci.com/Redcart/helda)
[![Codecov test coverage](https://codecov.io/gh/Redcart/helda/branch/master/graph/badge.svg)](https://codecov.io/gh/Redcart/helda?branch=master)
[![Documentation](https://www.rdocumentation.org/badges/version/helda)](https://www.rdocumentation.org/packages/helda)
[![License: GPL v3](https://img.shields.io/badge/license-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
<!-- badges: end -->

## Overview

This package provides functionalities that aim at facilitating and saving time when analysing data.

## Installation

You can install helda from CRAN by simply running:
```{r, eval = FALSE}
install.packages("helda")
```

## Development version

To get a bug fix, or use a feature from the development version, you can install 
helda from this GitHub repository.

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("Redcart/helda")
```

## Usage

This is a quick introduction to the lift curve function of the package:
```{r lift_curve, message = FALSE}
library(helda)

data_training <- titanic_training
data_validation <- titanic_validation

model_glm <- glm(formula = "Survived ~ Pclass + Sex + Age + SibSp + Fare + Embarked",
                 data = data_training,
                 family = binomial(link = "logit"))

predictions <- predict(object = model_glm, newdata = titanic_validation, type = "response")

plot <- lift_curve(predictions = predictions, true_labels = titanic_validation$Survived, 
                   positive_label = 1)

plot
```

## Getting help

If you encounter a clear bug, please file a minimal reproducible example on the [issues section](https://github.com/Redcart/helda/issues) of the repository.


## Author

Simon Corde

simon.corde[at]hotmail.fr
